---
title: 'Scrum Cycle 05: Working in Python or R'
author: "Code Crusaders"
date: "4/28/2020"
output:
  powerpoint_presentation: default
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  tidy = TRUE,
  tidy.opts=list(blank=FALSE, width.cutoff=60,size = 'tiny'))
library(knitr)
library(papeR)
#library(kableExtra)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

```{r loading, echo=FALSE}
bank.data <- read.csv(file = "cohort2020-set-a.csv", stringsAsFactors = TRUE, header = TRUE, sep = ',', na.strings = c("", "NA"))
```

## Slide with R Output

```{r data-summary, comment=""}
kable(summary(bank.data)[,0:6])
```

## Summary Cont'd

```{r, comment=""}
kable(summary(bank.data)[,0:-6])
```

## Box Plot of Age feature

```{r pressure}
boxplot(bank.data$age)
```

